Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
reformulate MFCCs description

Different sets of parameters were tested to compute the MFCCs. Results here are only reported for the best setting, which consisted of $40$ MFCCs (including the first energy coefficient) computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. This setting gives us $600$ feature vectors per scene. To get a more robust representation of lower dimensionality a pooling step is performed on the MFCCs: each recording is divided into $n$ non-overlapping $t$-seconds long ``texture'' windows. The MFCC vectors within each texture window are then averaged in time. As the \emph{ob} approaches involve a clustering step, we need to ensure that both MFCCs and scattering coefficients have a comparable number of vectors per recording. \ja{Why do we need to do this?} Thus, $t$ is set to $250\,\mathrm{ms}$, resulting in $120$ MFCCs texture windows per scene.

@@

Within a supervised setting of acoustic scene classification (ASC), we have shown the comparative benefits of log-scattering features over MFCCs, of majority voting at a mid-level time scale of $T=372\,\mathrm{ms}$ over prediction at a high-level time scale of $T=24\,\mathrm{ms}$, and of an adapted Gaussian kernel over the linear kernel in support vector machine (SVM) classification.
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}

>>>>

MFCCs are computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. Different ranks of coefficients were tested to compute the MFCCs, results here are only reported for the best setting, which consisted of $40$ MFCCs, including the first coefficient related to the average energy. This setting gives us $600$ feature vectors per scene. To get a more robust representation of lower dimensionality a pooling step is performed on the MFCCs: each recording is divided into $n$ non-overlapping $t$-seconds long ``texture'' windows. The MFCC vectors within each texture window are then averaged in time. As the \emph{ob} approaches involve a clustering step, we need to ensure that both MFCCs and scattering coefficients have a comparable number of vectors per recording. \ja{Why do we need to do this?} Thus, $t$ is set to $250\,\mathrm{ms}$, resulting in $120$ MFCCs texture windows per scene.

@@

\ml{Vincent: un par pour resumer la partie classif}
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}
